Graph-based Neuron Agglomeration using 3D Skeletons

### 2017-11-10 papers/cvpr2018/paper.tex
paper: Major improvements to evaluation
Add supplemental material template.
added some figures

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{algpseudocode}
\usepackage{algorithmicx}

@@

\def\cvprPaperID{446} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

@@

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{algpseudocode}
\usepackage{algorithmicx}
\usepackage{siunitx}

@@

\def\cvprPaperID{0446} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

@@

\begin{figure}[t]\footnotesize
	\vspace{-2.04in}
	\newcommand{\FigureWidth}{0.23\textwidth}
	\newcommand{\FigureShift}{\hspace{-0.42cm}}
	\newcommand{\figureShift}{\hspace{-0.3cm}}
	\begin{minipage}{\textwidth}
		\begin{center}
			\begin{tabular}{cccc}
				\FigureShift \includegraphics[width=\FigureWidth]{figures/schema/teaser-image.png} \includegraphics[width=\FigureWidth]{figures/schema/teaser-segmentation.png} &
				\FigureShift \includegraphics[width=\FigureWidth]{figures/schema/pre-multicut.png} &
				\FigureShift \includegraphics[width=\FigureWidth]{figures/schema/multicut-graph.png}&
				\FigureShift \includegraphics[width=\FigureWidth]{figures/schema/post-multicut.png}\\
				\figureShift (a) Input & \FigureShift (b)  Our results & \FigureShift(c) Dark channel of (a) & \FigureShift (d) Dark channel of (b)\\
			\end{tabular}
		\end{center}
		\vspace{-3mm}
		\caption{Deblurring result on a challenging low-light image. The blur process makes the dark channel of the blurred image less sparse~(c). Enforcing sparsity on the dark channel of the recovered image favors clean images over blurred ones.}
		\label{fig:teaser}
		%
	\end{minipage}
\end{figure}
